\cvsection{Projects}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {3D modelling, graphical interfaces, logical programming}   
    {\href{https://github.com/Educorreia932/LAIG/tree/master/TP3}{Green}}   
    {}        
    {Sep. 2020 - Jan. 2020}  
    {
      \begin{cvitems}
        \item {A web implementation of the game Green, a two-player tabletop game.}
      \end{cvitems}
    }
  
  \cventry
    {Software engineering, mobile development, UI/UX design, Agile, databases}   
    {\href{https://github.com/Educorreia932/ESOF}{Ask Away}}   
    {}        
    {Sep. 2020 - Dec. 2020}  
    {
      \begin{cvitems}
        \item {A mobile application, developed using Flutter, for attendees to ask questions in conference talks.}
      \end{cvitems}
    }
    
  \cventry
    {Object-Oriented Programming, design patterns, SOLID principles}  
    {\href{https://github.com/Educorreia932/LPOO/tree/master/Project}{Pokémon - A Sequel Coming In Inevitably}}   
    {}        
    {Sep. 2020 - Dec. 2020}  
    {
      \begin{cvitems}
        \item {Pokémon Fire Red look-alike game running on a terminal, written in Java.}
        \item {I'm quite proud of this project, given the fact I implemented a full-fledged sprite based graphical interface despite the limitations of using a terminal emulator and also because it faithfully recreated the Pokémon combat system from the original game.}
      \end{cvitems}
    } 
  
  \cventry
    {Web servers, web frameworks, web APIs}   
    {\href{https://educorreia932.dev/spotify_statistics}{Spotify Statistics}}   
    {}        
    {Aug. 2020} 
    {
      \begin{cvitems}
        \item {A webpage giving information about the favorite music genres of a person given their Spotify listening history.}
        \item {It obtained a considerable popularity and counted with more than \textbf{300.000} users at one point using it.}
      \end{cvitems}
    }
    
  \cventry
    {Data structures, algorithms, graphs, graphical interfaces}   
    {\href{https://github.com/Educorreia932/CAL}{Tour Mate App}}   
    {}        
    {Mar. 2020 - Jun. 2020}  
    {
      \begin{cvitems}
        \item {A C++ application that let's you plan a tour around Porto by choosing several touristic attractions and calculating an optimal route to let you visit them.}
      \end{cvitems}
    }
    
  \cventry
    {Game development, driver and low-level programming, computer communication}   
    {\href{https://github.com/Educorreia932/LCOM/tree/master/proj}{Project Watt}}   
    {}        
    {Sep. 2019 - Jan. 2020}  
    {
      \begin{cvitems}
        \item {A platformer game, written in C from scratch, with different gamemodes (single and multiplayer), including a campaign in which the player had to reach a goal at the end of the stage with puzzle and agility skills, and an arcade gamemode, very similar to Flappy Bird.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
